### 2016-02-11 reviews/answer_to_revieweres.txt

> Line 134: Why were these values (4 and 11) were chosen? I do not see the rational of taking 4 for a heterozygote and 11 for homozygote - shouldn’t these be the reverse?

ANSWER: this is a common practice in GBS SNP calling. We updated the text, added references to other works doing the same, and added a section in supplementary material explaining a bit of the related math. The short answer is that no, it's in general more difficult to call a homozygote, so you want to have more reads.

> Line 135-139: The reduction from 5 genotypic classes to 3 genotypic classes in alfalfa is a critical simplification step. There is no justification why this step was executed. My assumption is that this is because of the (software) methods that were used. The explanation and justification should be provided here. I am wondering whether the four general methods could be applied to the 5 genotypic classes – was this considered/studied?

ANSWER: the 5-to-3 reduction is not strictly related to algorithms. In fact, the general algorithms would work easily on any number of classes: MNI, SVDI and RFI would produce continuous values in the [0-4] range, and KNNI is naturally oriented toward a discrete outputs. Beagle and FILLIN, on the other hand, are less flexible, and using them on tetraploid genotypes is not straightforward.
However, the main reason for the simplification of heterozygotes is the available GBS read depth. To be able to call the heterozygote dosage it is required a high number of reads per locus, and accepting only the markers with enough reads highly reduces their number. We explained the choice in the proper M&M section and added reference to papers following this (common) practice.

### 2016-02-11 inputs/abstract.tex

\begin{abstract}
Genotyping-by-sequencing (GBS) is a rapid and cost-effective genome-wide 
genotyping technique applicable whether a reference genome is available 
or not. Due to the cost-coverage trade-off, however, GBS typically produces 
large amounts of missing marker genotypes, whose imputation becomes therefore 
both challenging and critical for later analyses.\\
In this work, the performance of four general imputation methods (K-Nearest 
Neighbors, Random Forest, Singular Value Decomposition, and Mean Value)
and two genotype-specific method (``Beagle'' and FILLIN) were measured 
on GBS data from alfalfa (\emph{Medicago sativa}, autotetraploid, heterozygous, 
without reference genome) and 
rice (\emph{Oryza sativa}, diploid, 100\% homozygous, with reference genome). Benchmarks 
consisted in progressive data filtering for marker call-rate (up to 70\%) and increasing 
proportions (up to 20\%) of known genotypes masked for imputation. The 
relative performance was measured as the total proportion of correctly imputed 
genotypes, globally and within each genotype class (two homozygotes in rice, 
two homozygotes and one heterozygote in alfalfa). Imputation efficiency was 
measured with computation times.\\
In general imputation accuracy was robust to increasing 
missing rates, and consistently higher in rice than in alfalfa. Accuracy 
was as high as 90-100\% for the major (most frequent) homozygous genotype, but dropped 
to 80-90\% (rice) and below 30\% (alfalfa) on the minor homozygous genotype. 
Beagle was the best performing method, both accuracy- 
and time-wise, when using a reference genome. When no reference 
genome was available, KNNI and RFI gave the highest accuracies, with KNNI 
being much faster.

>>>>

\begin{abstract}
Genotyping-by-sequencing (GBS) is a rapid and cost-effective genome-wide 
genotyping technique applicable whether a reference genome is available 
or not. Due to the cost-coverage trade-off, however, GBS typically produces 
large amounts of missing marker genotypes, whose imputation becomes therefore 
both challenging and critical for later analyses.\\
In this work, the performance of four general imputation methods (K-Nearest 
Neighbors, Random Forest, Singular Value Decomposition, and Mean Value)
and two genotype-specific method (``Beagle'' and FILLIN) were measured 
on GBS data from alfalfa (\emph{Medicago sativa L.}, autotetraploid, heterozygous, 
without reference genome) and 
rice (\emph{Oryza sativa L.}, diploid, 100\% homozygous, with reference genome). Benchmarks 
consisted in progressive data filtering for marker call-rate (up to 70\%) and increasing 
proportions (up to 20\%) of known genotypes masked for imputation. The 
relative performance was measured as the total proportion of correctly imputed 
genotypes, globally and within each genotype class (two homozygotes in rice, 
two homozygotes and one heterozygote in alfalfa). Imputation efficiency was 
measured with computation times.\\
In general imputation accuracy was robust to increasing 
missing rates, and consistently higher in rice than in alfalfa. Accuracy 
was as high as 90-100\% for the major (most frequent) homozygous genotype, but dropped 
to 80-90\% (rice) and below 30\% (alfalfa) on the minor homozygous genotype. 
Beagle was the best performing method, both accuracy- 
and time-wise, when using a reference genome. When no reference 
genome was available, KNNI and RFI gave the highest accuracies, with KNNI 
being much faster.

### 2016-02-11 inputs/results.tex

The imputation accuracy varied across the different genotype classes, with the highest accuracy in the most common genotype class (averaging \textcolor{red}{XXX}\% and \textcolor{red}{XXX}\% in alfalfa and rice, respectively), while the least common genotype class showed much lower accuracy (averaging \textcolor{red}{XXX}\% and \textcolor{red}{XXX}\% in alfalfa and rice, respectively).
Alfalfa datasets included heterozygous SNP loci, accounting for an average of 30\% of individuals per locus (Table~\ref{tab:descriptive_statistics}). Heterozygotes had an intermediate imputation accuracy ranging from 0\% with MNI to 70\% with KNNI. Results for each individual alfalfa population and the 12 individual rice chromosomes are similar to those discussed here (see Supplementary Figures S2 to S16). \\
Missing data did not affect the imputation accuracy substantially, with most algorithms showing a flat or almost flat response to increased missing rate. KNNI showed a decreasing imputation accuracy with increasing missing data, both in alfalfa and rice.

@@

When examining general imputation methods, resulting accuracies highlighted RFI and KNNI as the best ones. The two methods had comparable performances, without a preferable option over all experiments. SVDI followed, and MNI ranked last.\\
In Rice, for 70\% allowed missing rate datasets, the imputation accuracy of RFI was still greater than 90\%, while it dropped towards 75\% for KNNI and SVDI. As expected, MNI had an imputation accuracy of 100\% in the major homozygous class, but dropped to 0\% in the minor homozygous class.\\
In alfalfa KNNI showed the highest imputation accuracy over all classes \textcolor{red}{(XXX\%)} and in the heterozygous \textcolor{red}{(XXX\%)} and minor homozygous \textcolor{red}{(XXX\%)} genotype classes (Figure~\ref{fig:accuracy_alfalfa}). RFI and SVDI were second ranking. They did not differ much from MNI in the overall accuracy \textcolor{red}{(XXX\%)} and in the major \textcolor{red}{(XXX\%)} homozygous class, but gave higher imputation accuracy in the heterozygous \textcolor{red}{(XXX\%)} and minor homozygous \textcolor{red}{(XXX\%)} classes.

>>>>

The imputation accuracy varied across the different genotype classes, with the highest accuracy in the most common genotype class (averaging 92.27\% and 96.47\% in alfalfa and rice, respectively), while the least common genotype class showed much lower accuracy (averaging 5.79\% and 69.88\% in alfalfa and rice, respectively).
Alfalfa datasets included heterozygous SNP loci, accounting for an average of 30\% of individuals per locus (Table~\ref{tab:descriptive_statistics}). Heterozygotes had an intermediate imputation accuracy ranging from 0\% with MNI to 70\% with KNNI. Results for each individual alfalfa population and the 12 individual rice chromosomes are similar to those discussed here (see Supplementary Figures S2 to S16). \\
Missing data did not affect the imputation accuracy substantially, with most algorithms showing a flat or almost flat response to increased missing rate. KNNI showed a decreasing imputation accuracy with increasing missing data, both in alfalfa and rice.

@@

When examining general imputation methods, resulting accuracies highlighted RFI and KNNI as the best ones. The two methods had comparable performances, without a preferable option over all experiments. SVDI followed, and MNI ranked last.\\
In Rice, for 70\% allowed missing rate datasets, the imputation accuracy of RFI was still greater than 90\%, while it dropped towards 75\% for KNNI and SVDI. As expected, MNI had an imputation accuracy of 100\% in the major homozygous class, but dropped to 0\% in the minor homozygous class.\\
In alfalfa KNNI showed the highest imputation accuracy over all classes (averaging 82.20\%) and in the heterozygous (66.02\%) and minor homozygous (14.68\%) genotype classes (Figure~\ref{fig:accuracy_alfalfa}). RFI and SVDI were second ranking. They did not differ much from MNI in the overall accuracy (MNI: 78.38\%, RFI: 79.50\%, SVDI: 77.35\%) and in the major (MNI: 88.68\%, RFI: 89.05\%, SVDI 85.81\%) homozygous class, but gave higher imputation accuracy in the heterozygous (MNI: 58.87\%, RFI: 61.75\%, SVDI 61.67\%). On minor homozygous class only SVDI resulted in some sporadic correct imputation, while RFI and MNI did not produce any sensible result (MNI: 0\%, RFI: 0.01\%, SVDI 4.46\%) classes.

### 2016-02-11 inputs/supplementary.tex
phrasing

Where $N_h$ is the minimum number of reads required to label a stack of aligning reads as heterozygote. The discussed case of $N_h = 11$ brings to a total expected $HET \rightarrow HOM$ error rate of 4.22\%.\\
The hypothesis mentioned above greatly simplyfies the real case (e.g. $HOM \rightarrow HET$ errors can not happen, since a homozigote will always produce 100\% of reads of the same type). When accounting sequencing errors and reads quality a term for $HOM \rightarrow HET$ appears, due to reads sequences as the wrong allele. In the presented study we thus applied a threshold of 4 required reads per stack to call a homozigote to minimize this kind of error.

@@

\begin{figure}\includegraphics[width=0.95\textwidth]{SupplFig02_Alfalfa-Med.pdf}\caption{
imputation accuracies overall, for the major homozygous genotype (AA), for heterozygotes (AB), and for the minor homozygous genotype (BB) in datasets consisting of
10\%, 20\%, 40\% and 70\% allowed missing data per locus (boxes) with 1\%, 5\%, 10\% and 20\%
additional missing values artificially introduced (x-axis) for alfalfa population Alfalfa-Med.
Lines colors represent the five imputation algorithms: MNI
(orange), KNNI (red), SVDI (blue), RFI (green) and Beagle (black)}\end{figure}
\begin{figure}\includegraphics[width=0.95\textwidth]{SupplFig03_Alfalfa-PV.pdf}\caption{
imputation accuracies overall, for the major homozygous genotype (AA), for heterozygotes (AB), and for the minor homozygous genotype (BB) in datasets consisting of
10\%, 20\%, 40\% and 70\% allowed missing data per locus (boxes) with 1\%, 5\%, 10\% and 20\%
additional missing values artificially introduced (x-axis) for alfalfa population Alfalfa-PV.
Lines colors represent the five imputation algorithms: MNI
(orange), KNNI (red), SVDI (blue), RFI (green) and Beagle (black)}\end{figure}
\begin{figure}\includegraphics[width=0.95\textwidth]{SupplFig04_Rice-chrom-1.pdf}\caption{
imputation accuracies overall, for the major homozygous genotype (AA) and for the minor homozygous genotype (BB) in datasets consisting of
10\%, 20\%, 40\% and 70\% allowed missing data per locus (boxes) with 1\%, 5\%, 10\% and 20\%
additional missing values artificially introduced (x-axis) for rice chromosome 1 data.
Lines colors represent the five imputation algorithms: MNI
(orange), KNNI (red), SVDI (blue), RFI (green) and Beagle (black)}\end{figure}
\begin{figure}\includegraphics[width=0.95\textwidth]{SupplFig05_Rice-chrom-2.pdf}\caption{
imputation accuracies overall, for the major homozygous genotype (AA) and for the minor homozygous genotype (BB) in datasets consisting of
10\%, 20\%, 40\% and 70\% allowed missing data per locus (boxes) with 1\%, 5\%, 10\% and 20\%
additional missing values artificially introduced (x-axis) for rice chromosome 2 data.
Lines colors represent the five imputation algorithms: MNI
(orange), KNNI (red), SVDI (blue), RFI (green) and Beagle (black)}\end{figure}
\begin{figure}\includegraphics[width=0.95\textwidth]{SupplFig06_Rice-chrom-3.pdf}\caption{
imputation accuracies overall, for the major homozygous genotype (AA) and for the minor homozygous genotype (BB) in datasets consisting of
10\%, 20\%, 40\% and 70\% allowed missing data per locus (boxes) with 1\%, 5\%, 10\% and 20\%
additional missing values artificially introduced (x-axis) for rice chromosome 3 data.
Lines colors represent the five imputation algorithms: MNI
(orange), KNNI (red), SVDI (blue), RFI (green) and Beagle (black)}\end{figure}
\begin{figure}\includegraphics[width=0.95\textwidth]{SupplFig07_Rice-chrom-4.pdf}\caption{
imputation accuracies overall, for the major homozygous genotype (AA) and for the minor homozygous genotype (BB) in datasets consisting of
10\%, 20\%, 40\% and 70\% allowed missing data per locus (boxes) with 1\%, 5\%, 10\% and 20\%
additional missing values artificially introduced (x-axis) for rice chromosome 4 data.
Lines colors represent the five imputation algorithms: MNI
(orange), KNNI (red), SVDI (blue), RFI (green) and Beagle (black)}\end{figure}
\begin{figure}\includegraphics[width=0.95\textwidth]{SupplFig08_Rice-chrom-5.pdf}\caption{
imputation accuracies overall, for the major homozygous genotype (AA) and for the minor homozygous genotype (BB) in datasets consisting of
10\%, 20\%, 40\% and 70\% allowed missing data per locus (boxes) with 1\%, 5\%, 10\% and 20\%
additional missing values artificially introduced (x-axis) for rice chromosome 5 data.
Lines colors represent the five imputation algorithms: MNI
(orange), KNNI (red), SVDI (blue), RFI (green) and Beagle (black)}\end{figure}
\begin{figure}\includegraphics[width=0.95\textwidth]{SupplFig09_Rice-chrom-6.pdf}\caption{
imputation accuracies overall, for the major homozygous genotype (AA) and for the minor homozygous genotype (BB) in datasets consisting of
10\%, 20\%, 40\% and 70\% allowed missing data per locus (boxes) with 1\%, 5\%, 10\% and 20\%
additional missing values artificially introduced (x-axis) for rice chromosome 6 data.
Lines colors represent the five imputation algorithms: MNI
(orange), KNNI (red), SVDI (blue), RFI (green) and Beagle (black)}\end{figure}
\begin{figure}\includegraphics[width=0.95\textwidth]{SupplFig10_Rice-chrom-7.pdf}\caption{
imputation accuracies overall, for the major homozygous genotype (AA) and for the minor homozygous genotype (BB) in datasets consisting of
10\%, 20\%, 40\% and 70\% allowed missing data per locus (boxes) with 1\%, 5\%, 10\% and 20\%
additional missing values artificially introduced (x-axis) for rice chromosome 7 data.
Lines colors represent the five imputation algorithms: MNI
(orange), KNNI (red), SVDI (blue), RFI (green) and Beagle (black)}\end{figure}
\begin{figure}\includegraphics[width=0.95\textwidth]{SupplFig11_Rice-chrom-8.pdf}\caption{
imputation accuracies overall, for the major homozygous genotype (AA) and for the minor homozygous genotype (BB) in datasets consisting of
10\%, 20\%, 40\% and 70\% allowed missing data per locus (boxes) with 1\%, 5\%, 10\% and 20\%
additional missing values artificially introduced (x-axis) for rice chromosome 8 data.
Lines colors represent the five imputation algorithms: MNI
(orange), KNNI (red), SVDI (blue), RFI (green) and Beagle (black)}\end{figure}
\begin{figure}\includegraphics[width=0.95\textwidth]{SupplFig12_Rice-chrom-9.pdf}\caption{
imputation accuracies overall, for the major homozygous genotype (AA) and for the minor homozygous genotype (BB) in datasets consisting of
10\%, 20\%, 40\% and 70\% allowed missing data per locus (boxes) with 1\%, 5\%, 10\% and 20\%
additional missing values artificially introduced (x-axis) for rice chromosome 9 data.
Lines colors represent the five imputation algorithms: MNI
(orange), KNNI (red), SVDI (blue), RFI (green) and Beagle (black)}\end{figure}
\begin{figure}\includegraphics[width=0.95\textwidth]{SupplFig13_Rice-chrom-10.pdf}\caption{
imputation accuracies overall, for the major homozygous genotype (AA) and for the minor homozygous genotype (BB) in datasets consisting of
10\%, 20\%, 40\% and 70\% allowed missing data per locus (boxes) with 1\%, 5\%, 10\% and 20\%
additional missing values artificially introduced (x-axis) for rice chromosome 10 data.
Lines colors represent the five imputation algorithms: MNI
(orange), KNNI (red), SVDI (blue), RFI (green) and Beagle (black)}\end{figure}
\begin{figure}\includegraphics[width=0.95\textwidth]{SupplFig14_Rice-chrom-11.pdf}\caption{
imputation accuracies overall, for the major homozygous genotype (AA) and for the minor homozygous genotype (BB) in datasets consisting of
10\%, 20\%, 40\% and 70\% allowed missing data per locus (boxes) with 1\%, 5\%, 10\% and 20\%
additional missing values artificially introduced (x-axis) for rice chromosome 11 data.
Lines colors represent the five imputation algorithms: MNI
(orange), KNNI (red), SVDI (blue), RFI (green) and Beagle (black)}\end{figure}
\begin{figure}\includegraphics[width=0.95\textwidth]{SupplFig15_Rice-chrom-12.pdf}\caption{
imputation accuracies overall, for the major homozygous genotype (AA) and for the minor homozygous genotype (BB) in datasets consisting of
10\%, 20\%, 40\% and 70\% allowed missing data per locus (boxes) with 1\%, 5\%, 10\% and 20\%
additional missing values artificially introduced (x-axis) for rice chromosome 12 data.
Lines colors represent the five imputation algorithms: MNI
(orange), KNNI (red), SVDI (blue), RFI (green) and Beagle (black)}\end{figure}
\begin{figure}\includegraphics[width=0.95\textwidth]{SupplFig16_Rice.pdf}\caption{
imputation accuracies overall, for the major homozygous genotype (AA) and for the minor homozygous genotype (BB) in datasets consisting of
10\%, 20\%, 40\% and 70\% allowed missing data per locus (boxes) with 1\%, 5\%, 10\% and 20\%
additional missing values artificially introduced (x-axis) for whole rice data set.
Lines colors represent the five imputation algorithms: MNI
(orange), KNNI (red), SVDI (blue), RFI (green) and Beagle (black)}\end{figure}

>>>>

Where $N_h$ is the minimum number of reads required to label a stack of aligning reads as heterozygote. The discussed case of $N_h = 11$ brings to a total expected $HET \rightarrow HOM$ error rate of 4.22\%.\\
The hypothesis mentioned above greatly simplyfies the real case (e.g. $HOM \rightarrow HET$ errors can not happen, since a homozigote will always produce 100\% of reads of the same type). When accounting sequencing errors and reads quality a term for $HOM \rightarrow HET$ appears, due to reads sequenced as the wrong allele. In the presented study we thus applied a threshold of 4 required reads per stack to call a homozigote to minimize this kind of error.

@@

\begin{figure}\includegraphics[width=0.95\textwidth]{figure_reforma.pdf}\caption{
imputation accuracies overall, for the major homozygous genotype (AA), for heterozygotes (AB), and for the minor homozygous genotype (BB) in datasets consisting of
10\%, 20\%, 40\% and 70\% allowed missing data per locus (boxes) with 1\%, 5\%, 10\% and 20\%
additional missing values artificially introduced (x-axis) for alfalfa population Alfalfa-Med.
Lines colors represent the five imputation algorithms: MNI (salmon), KNNI (red), SVDI (blue), RFI (green), Beagle with ordered markers (solid black) and Beagle with unordered markers (dashed black)}\end{figure}

\begin{figure}\includegraphics[width=0.95\textwidth]{figure_lodi.pdf}\caption{
imputation accuracies overall, for the major homozygous genotype (AA), for heterozygotes (AB), and for the minor homozygous genotype (BB) in datasets consisting of
10\%, 20\%, 40\% and 70\% allowed missing data per locus (boxes) with 1\%, 5\%, 10\% and 20\%
additional missing values artificially introduced (x-axis) for alfalfa population Alfalfa-PV.
Lines colors represent the five imputation algorithms: MNI (salmon), KNNI (red), SVDI (blue), RFI (green), Beagle with ordered markers (solid black) and Beagle with unordered markers (dashed black)}\end{figure}

\begin{figure}\includegraphics[width=0.95\textwidth]{figure_rice_chrom_1.pdf}\caption{
imputation accuracies overall, for the major homozygous genotype (AA) and for the minor homozygous genotype (BB) in datasets consisting of
10\%, 20\%, 40\% and 70\% allowed missing data per locus (boxes) with 1\%, 5\%, 10\% and 20\%
additional missing values artificially introduced (x-axis) for rice chromosome 1 data.
Lines colors represent the five imputation algorithms: MNI (salmon), KNNI (red), SVDI (blue), RFI (green), Beagle with ordered markers (solid black) and Beagle with unordered markers (dashed black)}\end{figure}

\begin{figure}\includegraphics[width=0.95\textwidth]{figure_rice_chrom_2.pdf}\caption{
imputation accuracies overall, for the major homozygous genotype (AA) and for the minor homozygous genotype (BB) in datasets consisting of
10\%, 20\%, 40\% and 70\% allowed missing data per locus (boxes) with 1\%, 5\%, 10\% and 20\%
additional missing values artificially introduced (x-axis) for rice chromosome 2 data.
Lines colors represent the five imputation algorithms: MNI (salmon), KNNI (red), SVDI (blue), RFI (green), Beagle with ordered markers (solid black) and Beagle with unordered markers (dashed black)}\end{figure}

\begin{figure}\includegraphics[width=0.95\textwidth]{figure_rice_chrom_3.pdf}\caption{
imputation accuracies overall, for the major homozygous genotype (AA) and for the minor homozygous genotype (BB) in datasets consisting of
10\%, 20\%, 40\% and 70\% allowed missing data per locus (boxes) with 1\%, 5\%, 10\% and 20\%
additional missing values artificially introduced (x-axis) for rice chromosome 3 data.
Lines colors represent the five imputation algorithms: MNI (salmon), KNNI (red), SVDI (blue), RFI (green), Beagle with ordered markers (solid black) and Beagle with unordered markers (dashed black)}\end{figure}

\begin{figure}\includegraphics[width=0.95\textwidth]{figure_rice_chrom_4.pdf}\caption{
imputation accuracies overall, for the major homozygous genotype (AA) and for the minor homozygous genotype (BB) in datasets consisting of
10\%, 20\%, 40\% and 70\% allowed missing data per locus (boxes) with 1\%, 5\%, 10\% and 20\%
additional missing values artificially introduced (x-axis) for rice chromosome 4 data.
Lines colors represent the five imputation algorithms: MNI (salmon), KNNI (red), SVDI (blue), RFI (green), Beagle with ordered markers (solid black) and Beagle with unordered markers (dashed black)}\end{figure}

\begin{figure}\includegraphics[width=0.95\textwidth]{figure_rice_chrom_5.pdf}\caption{
imputation accuracies overall, for the major homozygous genotype (AA) and for the minor homozygous genotype (BB) in datasets consisting of
10\%, 20\%, 40\% and 70\% allowed missing data per locus (boxes) with 1\%, 5\%, 10\% and 20\%
additional missing values artificially introduced (x-axis) for rice chromosome 5 data.
Lines colors represent the five imputation algorithms: MNI (salmon), KNNI (red), SVDI (blue), RFI (green), Beagle with ordered markers (solid black) and Beagle with unordered markers (dashed black)}\end{figure}

\begin{figure}\includegraphics[width=0.95\textwidth]{figure_rice_chrom_6.pdf}\caption{
imputation accuracies overall, for the major homozygous genotype (AA) and for the minor homozygous genotype (BB) in datasets consisting of
10\%, 20\%, 40\% and 70\% allowed missing data per locus (boxes) with 1\%, 5\%, 10\% and 20\%
additional missing values artificially introduced (x-axis) for rice chromosome 6 data.
Lines colors represent the five imputation algorithms: MNI (salmon), KNNI (red), SVDI (blue), RFI (green), Beagle with ordered markers (solid black) and Beagle with unordered markers (dashed black)}\end{figure}

\begin{figure}\includegraphics[width=0.95\textwidth]{figure_rice_chrom_7.pdf}\caption{
imputation accuracies overall, for the major homozygous genotype (AA) and for the minor homozygous genotype (BB) in datasets consisting of
10\%, 20\%, 40\% and 70\% allowed missing data per locus (boxes) with 1\%, 5\%, 10\% and 20\%
additional missing values artificially introduced (x-axis) for rice chromosome 7 data.
Lines colors represent the five imputation algorithms: MNI (salmon), KNNI (red), SVDI (blue), RFI (green), Beagle with ordered markers (solid black) and Beagle with unordered markers (dashed black)}\end{figure}

\begin{figure}\includegraphics[width=0.95\textwidth]{figure_rice_chrom_8.pdf}\caption{
imputation accuracies overall, for the major homozygous genotype (AA) and for the minor homozygous genotype (BB) in datasets consisting of
10\%, 20\%, 40\% and 70\% allowed missing data per locus (boxes) with 1\%, 5\%, 10\% and 20\%
additional missing values artificially introduced (x-axis) for rice chromosome 8 data.
Lines colors represent the five imputation algorithms: MNI (salmon), KNNI (red), SVDI (blue), RFI (green), Beagle with ordered markers (solid black) and Beagle with unordered markers (dashed black)}\end{figure}

\begin{figure}\includegraphics[width=0.95\textwidth]{figure_rice_chrom_9.pdf}\caption{
imputation accuracies overall, for the major homozygous genotype (AA) and for the minor homozygous genotype (BB) in datasets consisting of
10\%, 20\%, 40\% and 70\% allowed missing data per locus (boxes) with 1\%, 5\%, 10\% and 20\%
additional missing values artificially introduced (x-axis) for rice chromosome 9 data.
Lines colors represent the five imputation algorithms: MNI (salmon), KNNI (red), SVDI (blue), RFI (green), Beagle with ordered markers (solid black) and Beagle with unordered markers (dashed black)}\end{figure}

\begin{figure}\includegraphics[width=0.95\textwidth]{figure_rice_chrom_10.pdf}\caption{
imputation accuracies overall, for the major homozygous genotype (AA) and for the minor homozygous genotype (BB) in datasets consisting of
10\%, 20\%, 40\% and 70\% allowed missing data per locus (boxes) with 1\%, 5\%, 10\% and 20\%
additional missing values artificially introduced (x-axis) for rice chromosome 10 data.
Lines colors represent the five imputation algorithms: MNI (salmon), KNNI (red), SVDI (blue), RFI (green), Beagle with ordered markers (solid black) and Beagle with unordered markers (dashed black)}\end{figure}
\begin{figure}\includegraphics[width=0.95\textwidth]{figure_rice_chrom_11.pdf}\caption{
imputation accuracies overall, for the major homozygous genotype (AA) and for the minor homozygous genotype (BB) in datasets consisting of
10\%, 20\%, 40\% and 70\% allowed missing data per locus (boxes) with 1\%, 5\%, 10\% and 20\%
additional missing values artificially introduced (x-axis) for rice chromosome 11 data.
Lines colors represent the five imputation algorithms: MNI (salmon), KNNI (red), SVDI (blue), RFI (green), Beagle with ordered markers (solid black) and Beagle with unordered markers (dashed black)}\end{figure}

\begin{figure}\includegraphics[width=0.95\textwidth]{figure_rice_chrom_12.pdf}\caption{
imputation accuracies overall, for the major homozygous genotype (AA) and for the minor homozygous genotype (BB) in datasets consisting of
10\%, 20\%, 40\% and 70\% allowed missing data per locus (boxes) with 1\%, 5\%, 10\% and 20\%
additional missing values artificially introduced (x-axis) for rice chromosome 12 data.
Lines colors represent the five imputation algorithms: MNI (salmon), KNNI (red), SVDI (blue), RFI (green), Beagle with ordered markers (solid black) and Beagle with unordered markers (dashed black)}\end{figure}

\begin{figure}\includegraphics[width=0.95\textwidth]{figure_rice.pdf}\caption{
imputation accuracies overall, for the major homozygous genotype (AA) and for the minor homozygous genotype (BB) in datasets consisting of
10\%, 20\%, 40\% and 70\% allowed missing data per locus (boxes) with 1\%, 5\%, 10\% and 20\%
additional missing values artificially introduced (x-axis) for whole rice data set.
Lines colors represent the five imputation algorithms: MNI (salmon), KNNI (red), SVDI (blue), RFI (green), Beagle with ordered markers (solid black) and Beagle with unordered markers (dashed black)}\end{figure}
